\section{Intellectual property}

Our approach to intellectual property (IP) diverges from conventional strategies that rely heavily on patents to protect innovations. 
In the realm of precision medicine, the true value lies not in restricting access to technology through patents but in fostering an environment of open innovation and sharing. 

\textbf{Open-source commitment:} We are committed to open-source code and documentation. This commitment supports our mission to advance scientific understanding and innovation in precision medicine. By making our methodologies and technologies publicly available, we enable a collaborative approach where researchers and practitioners can contribute to and benefit from our developments.

\textbf{Credibility and transparency:} We prioritise maintaining high credibility and transparency over the potential financial benefits of patenting our technology. Our stakeholders can value the openness which allows them to verify, adapt, and build upon our work. This transparency is crucial for driving innovation and trust in our processes and outcomes.

\textbf{Focus on innovation and utility:} While we do not dismiss the potential of commercialising discoveries made through our system, our primary focus remains on creating tools and systems that facilitate robust scientific research. We believe that leading through innovation and delivering superior products and services are more crucial for leadership in our field than the exclusive rights granted by patents.

\textbf{Industry perspective:} This philosophy aligns with trends observed in several leading technology companies, where the focus shifts from guarding IP through patents to leading through rapid innovation and open platforms. In these cases, the speed of innovation and the ability to outpace competitors often prove more valuable than traditional patent strategies.

By adopting this IP philosophy, we aim to cultivate a foundation that not only accelerates advancements in precision medicine but also supports a broader scientific community in making impactful discoveries that can lead to better healthcare outcomes worldwide.
