\section{Core philosophy}

At the \pmu we redefine translational medicine by adhering to a foundational philosophy that optimises our processes beyond merely implementing cutting-edge methods. This dedication ensures that every member and tool within our unit contributes towards a unified, efficient framework aimed at enhancing operational and medical precision.

\subsection*{The challenge}

Previously, our team faced significant delays due to inefficient collaboration and repetitive searches for essential data, such as patient statistics or file locations. These redundancies hindered our progress and diluted our focus.

\subsection*{Our approach}

\begin{enumerate}
\item \textbf{Unified structure}: We maintain a consistent framework for all projects under the Precision Medicine Unit, enhancing setup and integration.
\item \textbf{Single source of variables}: All project-related data is tracked via a centralised system, eliminating the need for repetitive searches.
\item \textbf{Standardised format}: We implement a uniform format across all operations to ensure quick and easy access to necessary information without confusion.
\end{enumerate}

\subsection*{The impact}

These strategies ensure seamless updates across projects when new data is integrated, akin to the efficiency of a robust digital codebase \citep{potvin_levenberg_google_ACM}. This system not only boosts our operational efficiency but also amplifies our capabilities in translational medicine.

\subsection*{Philosophy before tools}

We prioritise our strategic approach over specific tools. Our commitment to a single-source, everything-as-code philosophy necessitates the use of tools that support shared variables and robust data integration. We opt for industry-standard and preferably open-source options like Markdown, LaTeX, R, and Python, ensuring that core data remains secure and all software and document source codes are public. This philosophy not only streamlines our internal processes but also aligns with our translational medicine efforts, enabling more efficient and effective application of innovative clinical methods.
